Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-09-19 paper/related-work.tex
Resolve TODOs in conclusion

%% DO NOT REMOVE --- BUT FEEL FREE TO REVISE
%% Specifically requested by the reviewers to be included in this paper!!!
Another model based approach to secure system architectures follows a pattern similar to \brfcs\ with attestation by inserting pre-verified components into the architecture to give certain guarantees \cite{6209212}.
In that work, the data connections are annotated with security properties as are the components.
A secondary analysis determines if the components meet the security requirements of the data connections, and if not, inserts new security enhancing components in the connection.
The insertion algorithm considers time cost when inserting components to preserve worst-case execution times mandated by the system.
\brfcs\ has the ability to insert pre-verified components based on cyber-requirements, but does not currently have the ability to annotate connections with security properties or automatically infer where secure components need to be inserted. 
\TODO{not clear where our work has benefits compared to this.}

@@

A fully verified compiler has been developed that takes Lustre and compiles
it into assembly code, specified and verified in Coq \cite{10.1145/3140587.3062358}.
The key is in combining infinite sequences of data-flow models with incremental
manipulation of memories akin to an imperative model. CompCert is used on the
backend to create the final rendered executable \cite{compcert}.
This work is quite similar to
ours in providing a verified compilation chain from Lustre. However,
there are significant differences: notably, they tackle a more
comprehensive subset of Lustre than our work. We have been able to
work effectively with a relatively simple core language, \eg, without
\emph{clocking} features.  This subset aligns with our contract language, and
allows us to generate behaviorally equivalent code so we can show that the
generated code meets its logical specification.  This, in turn,
can be used as a leaf-level claim in a system-wide correctness argument
conducted by compositional reasoning in AGREE.
\TODO{not clear where the CompCert work falls short compared to ours.}

>>>>

%% DO NOT REMOVE --- BUT FEEL FREE TO REVISE
%% Specifically requested by the reviewers to be included in this paper!!!
Another model based approach to secure system architectures follows a pattern similar to \brfcs\ with attestation by inserting pre-verified components into the architecture to give certain guarantees \cite{6209212}.
In that work, the data connections are annotated with security properties as are the components.
A secondary analysis determines if the components meet the security requirements of the data connections, and if not, inserts new security enhancing components in the connection.
The insertion algorithm considers time cost when inserting components to preserve worst-case execution times mandated by the system.
In the \brfcs\ tool chain there are tools that can analyze the model annotated with security properties and identify where security vulnerabilities may be located, and there are other tools to transform the model to address those vulnerabilities such as those discussed in this paper.

has the ability to insert pre-verified components based on cyber-requirements, and it does have the ability to automatically infer where secure components need to be inserted based on the security properties of the components and annotations on the data connections.

@@

A fully verified compiler has been developed that takes Lustre and compiles
it into assembly code, specified and verified in Coq \cite{10.1145/3140587.3062358}.
The key is in combining infinite sequences of data-flow models with incremental
manipulation of memories akin to an imperative model. CompCert is used on the
backend to create the final rendered executable \cite{compcert}.
This work is quite similar to
ours in providing a verified compilation chain from Lustre. However,
there are significant differences: notably, they tackle a more
comprehensive subset of Lustre than our work. We have been able to
work effectively with a relatively simple core language, \eg, without
\emph{clocking} features.  This subset aligns with our contract language, and
allows us to generate behaviorally equivalent code so we can show that the
generated code meets its logical specification.  This, in turn,
can be used as a leaf-level claim in a system-wide correctness argument
conducted by compositional reasoning in AGREE. It is important to note that we target a wholistic systems approach to cyber-security that is integrated into the AGREE reasoning environment whereas the other work targets more specifically a compiler for Lustre.
